### 2019-05-22 doc/chapters/using_bitcoins.tex
more text

\section{Validation of a Transaction (with method checkTransaction)}

>>>>

\section{Validation of a Transaction (with method checkTransaction)}
Bitcoin-S-Core offers a function called \emph{checkTransaction}.
This is its type signature.
\begin{lstlisting}
  checkTransaction(transaction: Transaction): Boolean
\end{lstlisting}
It takes a transaction as input and returns a boolean whether the transaction is valid or not.
There are several checks in checkTransaction.
For example it checks if there is either no input or no output.
In this case it returns false.

The relevant parts for the property to be verified are the following two lines.
\begin{lstlisting}
  val prevOutputs = transaction.inputs.map(_.previousOutput)
  val noDuplicateInputs = prevOutputs.distinct.size == prevOutputs.size
\end{lstlisting}
It gathers all inputs output.
On this previous outputs it calls distinct and checks if the size stays the same.
Distinct removes duplicates, so if there was two times the same input the size of inputs before calling distinct would be greater.
